Open Software - Restricted Data:  A Suicide/Climate Case Study.

### 2015-12-02 report1_high_level/manuscript.Rmd
add Rmd to the report1 index.org
add stuff for report
modify the PDF link

\vspace{2mm}\hrule
\paragraph*{Background:} This essay was written to accompany the material presented as a
speedtalk and poster at the National Climate Change Adaptation
Research Facility Conference 'Climate Adaptation knowledge and
partnership', June 2013, Sydney.  The poster and slideshow are both available to download from this website: [http://opensoftware-restricteddata.github.io/presentations-nccarf-2013/](http://opensoftware-restricteddata.github.io/presentations-nccarf-2013/)

@@

\paragraph*{Results:} We built a safe Server/Client Computational
Environment for using open software with restricted data.  We
demonstrate the use of this system using drought and suicide as a case study.  
We describe the potential use of this system in modelling climate change scenarios.

>>>>

\vspace{2mm}\hrule
\paragraph*{Background:} This essay was written to accompany the material presented as a
speedtalk and poster at the National Climate Change Adaptation
Research Facility Conference 'Climate Adaptation knowledge and
partnership', June 2013, Sydney.  The poster and slideshow are both available to download from this website: [http://swish-climate-impact-assessment.github.io/opensoftware-restricteddata/presentations-nccarf-2013/](http://swish-climate-impact-assessment.github.io/opensoftware-restricteddata/presentations-nccarf-2013/)

@@

\paragraph*{Results:} We built a secure Server/Client Computational
Environment for using open software with restricted data.  We
demonstrate the use of this system using drought and suicide as a case study.  
We describe the potential use of this system in modelling climate change scenarios.
